%!TEX TS?program = pdflatexmk

% This is a "bare-bones" thesis template file.  For examples of how to
% use a few more LaTeX features, look in the 'sample' folder.  Read
% the User Guide for documentation of the 'fsuthesis' class features.
% Follow the FSU 'Guidelines and Requirements for Electronic Theses,
% Treatises, and Dissertations (ETDs)' document for all entries.

\documentclass[11pt,expanded,copyright]{fsuthesis}

% Additional packages may be loaded here.

\usepackage{amsmath, physics}
\usepackage{nicefrac}
\usepackage{siunitx}

\usepackage[acronyms]{glossaries}
\newacronym{co2}{CO2}{Carbon Dioxide}
\newacronym{sco2}{sCO2}{supercritical Carbon Dioxide}
\newacronym{les}{LES}{large eddy simulation}
\newacronym{fda}{FDA}{Food and Drug Administration}
\newacronym{dns}{DNS}{direct numerical simulation}
\newacronym{egs}{EGS}{Enhanced Geothermal Systems}
\newacronym{cfd}{CFD}{computational fluid dynamics}
\newacronym{rans}{RANS}{Reynolds-averaged Navier-Stokes}
\newacronym{sgs}{SGS}{subgrid-scale}
\newacronym{srk}{SRK EoS}{Soave-Redlich-Kwong Equation of State}
\newacronym{pr}{PR EoS}{Peng-Robinson Equation of State}
\newacronym{eos}{EoS}{Equation of State}
\newacronym{nist}{NIST}{National Institute of Standards and Technology}
\newacronym{hpc}{HPC}{high-performance computing}
\newacronym{smd}{SMD}{dynamic Smagorinsky}
\newacronym{ppm}{PPM}{piecewise parabolic method}
\newacronym{nrel}{NREL}{National Renewable Energy Laboratory}
\newacronym{rms}{rms}{root mean square}
\newacronym{amr}{AMR}{adaptive mesh refinement}
\newacronym{ecp}{ECP}{Exascale Computing Project}
\newacronym{doe}{DOE}{Department of Energy}
\newacronym{hmhw}{HMHW}{half-mean half-width}
\newacronym{tke}{TKE}{turbulent kinetic energy}
\newacronym{sdc}{SDC}{Spectral Deferred Correction}
\newacronym{mol}{MOL}{Method of Lines}
\newacronym{ode}{ODE}{ordinary differential equation}
\newacronym{pde}{PDE}{partial differential equation}
\newacronym{misdc}{MISDC}{multi-implicit spectral deferred correction}
\newacronym{cfl}{CFL}{Courant-Friedrichs-Lewy}
\newacronym{nscbc}{NSCBC}{Navier-Stokes Characteristic Boundary Conditions}
\newacronym{qssa}{QSSA}{quasi-steady state assumptions}

\makeglossaries

\ifpdf   % We execute this part (up to \else) if we are in PDF mode.
  \usepackage[pdftex]{graphicx}
  % We can create color text in our document using the color package.
  % We load it here so that we can tweak the default colors used in
  % the links created by hyperref, as the defaults are a bit too
  % bright and gaudy for an austere document such as this. ;-)
  % Note that the Manuscript Clearance Advisors will not allow any
  % colored text at all, so if you're using hyperref, you'll need to
  % set all the colors to black (or set colorlinks=false below).
  \usepackage{xcolor}
  \definecolor{mygreen}{rgb}{0,0.6,0}
  \definecolor{myblue}{rgb}{0.3,0.2,0.8}
  \definecolor{myred}{rgb}{0.8,0.1,0.1}
  
  % Define some colors
\definecolor{c1med}{HTML}{F15A60} % red
\definecolor{c2med}{HTML}{7AC36A} % green
\definecolor{c3med}{HTML}{5A9BD4} % blue
\definecolor{c4med}{HTML}{FAA75B} % orange
\definecolor{c5med}{HTML}{9E67AB} % purple
\definecolor{c6med}{HTML}{CE7058} % burgundy
\definecolor{c7med}{HTML}{D77FB4} % magenta
\definecolor{c8med}{HTML}{737373} % grey

\definecolor{c1brt}{HTML}{EE2E2F} % red     
\definecolor{c2brt}{HTML}{008C48} % green   
\definecolor{c3brt}{HTML}{185AA9} % blue    
\definecolor{c4brt}{HTML}{F47D23} % orange  
\definecolor{c5brt}{HTML}{662C91} % purple  
\definecolor{c6brt}{HTML}{A21D21} % burgundy
\definecolor{c7brt}{HTML}{B43894} % magenta 
\definecolor{c8brt}{HTML}{010202} % black
  % The hyperref package has lots of features and options.  If you
  % are interested in creating a state-of-the-art PDF document out
  % of your thesis/dissertation, you should read more about this
  % extremely useful package.
 \usepackage[colorlinks=false,bookmarks=true,pdfborder={0 0 0},
   linkcolor=myblue,urlcolor=myred,citecolor=mygreen,
    breaklinks=true,bookmarksnumbered=true]{hyperref}
\else    % Otherwise we'll run this part if we are not in PDF mode.
  \usepackage[dvips]{graphicx}
\fi

\usepackage{tikz}
\usetikzlibrary{hobby,calc,decorations.markings,arrows.meta,patterns}
\usepackage{subcaption}
\usepackage{float}
\usepackage[utf8]{inputenc} % usually not needed (loaded by default)
\usepackage[T1]{fontenc}


% Do NOT use 'geometry', 'setspace', or 'tocloft' packages! They will
% mess up the spacing provided by 'fsuthesis'.

% If using the BibLaTeX package for generating a bibliography or
% references section, uncomment the following 5 lines. This is a
% basic starting point, and you may want other package options.
% You'll also need to uncomment the '\printbibliography' line
% toward the end of this file. Refer to the biblatex package
% documentation for information. The file 'myrefs.bib' contains
% a few sample references. 

\usepackage[american]{babel}
\addto\captionsamerican{\renewcommand*{\contentsname}{Table of Contents}}
\usepackage{csquotes}
\usepackage{biblatex}
\addbibresource{myrefs.bib}

\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}


%\usepackage{cite}

%
% Update these entries. See the User Guide for more information.
%
% \title{Supercritical Carbon Dioxide Round Turbulent Jets:\protect\\ Using Large Eddy Simulations to Investigate Fundamental Flow Physics of Complex Fluids}
\title{Large Eddy Simulations to Investigate the Fundamental Flow Physics of Supercritical Carbon Dioxide Turbulent Jets}
\author{Julia Ream}
\college{College of Arts \& Sciences}
\department{Department of Mathematics}  % Delete if no department
\manuscripttype{Dissertation}              % [Thesis, Dissertation, Treatise]
\degree{Doctor of Philosophy}               % [Master of Science, Doctor of Philosophy...]  
\degreeyear{2023}
\defensedate{July 11, 2023}

%
% If creating a PDF, you may want to uncomment these and enter
% appropriate metadata for your document. See the User Guide.
%
%\subject{My Topic}
%\keywords{keyterm1; keyterm2; keyterm3; ...}
%

%
% Update to use the real names and positions of each person.
% See FSU's 'Guidelines and Requirements' document for the proper
% formats and titles.
%
\committeeperson{Mark Sussman}{Professor Co-Directing Dissertation}
\committeeperson{Marc Henry de Frahan}{Professor Co-Directing Dissertation}
\committeeperson{Bryan Quaife}{University Representative}
\committeeperson{Aseel Farhat}{Committee Member}
\committeeperson{Sanghyun Lee}{Committee Member}

\clubpenalty=9999
\widowpenalty=9999

\begin{document}

\frontmatter
\maketitle
\makecommitteepage

\begin{dedication}
\textit{
\begin{center}
\begin{tabular}{l}
All hail, Macbeth! hail to thee, thane of Glamis!	\\
All hail, Macbeth, hail to thee, thane of Cawdor!	 \\
All hail, Macbeth, thou shalt be king hereafter! \\
\end{tabular}
\end{center}
}
\begin{center}
\begin{tabular}{r}
Macbeth, \textit{Act I, Scene III}
\end{tabular}
\end{center}

\end{dedication}

\begin{acknowledgments}
I would like to first extend a hearty thanks my wonderful co-advisers, Dr.\ Mark Sussman and Dr.\ Marc Henry de Frahan. Dr.\ Sussman has given me an abundance of knowledge and memorable anecdotes in my eight years of learning from him, which I will cherish forever. He was the first person to suggest I apply to PhD programs when I initially started thinking about going to graduate school, so I really would not be here without his encouragement and support. I will also be forever grateful to Marc for all of the time, energy, guidance, knowledge, and advice that he has given me over these past four years. One day, I hope to be as good of a mentor to someone as he has been to me. I would also like to extend my deepest appreciation to my committee members: Dr.\ Aseel Farhat, Dr.\ Sanghyun Lee, and Dr.\ Bryan Quaife. Their feedback throughout this process has been invaluable. 

There are many people that have had a significant impact on my life who I met from the internships and graduate assistantships that I've held during my time at FSU. Many thanks to Michael Martin, Shashank Yellapantula, Anne Felden, and Marc Day for their mentorship and the collaborations they have fostered well beyond the end of our summers together. Special thanks are due to Dr.\ Penelope Kirby for being an exemplary leader and for trusting me with so many extraordinary teaching opportunities.  

This work would not have been possible without the support of my incredible friends. I am forever indebted to the besties I've made along the way: Virginia for bringing her personal brand of chaos and humor to our day-to-day antics since day one, Angie for always gassing me up and validating my Virgo tendencies, Matt for always giving me custody of our shared brain cell whenever I needed it most, Kyle for keeping my stomach and soul well-fed with our many nights of dinner and a movie, Colton for being the best dad a friend group could ever ask for, Sathya for his wisdom and insights into both math and life in general, and Austin for his trivia contributions and passionate opinions. I also extend my thanks to the plethora of other graduate students who greatly boosted morale over these past six years: Dan, Lydia, Devon, Celine, David, and the extensive members of Waldemar. Of course, many thanks are due to my non-graduate school people as well: Hannah, Lauren, Christina, Cam, and Goose. 

Finally, I owe everything to my family. My mom and dad, Maria and Jeff, have motivated me to do my best in school, always, whether it be in studying music, English, math or theatre. I would not be where I am today without their hard work and sacrifice. My brother, Jacob, and my cousins, Jessica and Bill, have also been in my corner since forever, and I am grateful to have always had them by my side. I was also lucky enough to have gained in-laws during my time in grad school whose love and support is also much appreciated. Though it may be odd, I feel compelled to also extend my gratitude to Tuna; she will never read this because she is a cat, but her contributions toward my mental health during this process cannot go unnoted. Last, but certainly not least, I extend my deepest gratitude to my husband, Alex. Even at my lowest lows, he believed in me so much that I had no choice but to believe in myself. Words cannot adequately express how grateful I am to have found him within all of this. 

This research was supported in part by an appointment with the National Science Foundation (NSF) Mathematical Sciences Graduate Internship (MSGI) Program sponsored by the NSF Division of Mathematical Sciences. This program is administered by the Oak Ridge Institute for Science and Education (ORISE) through an interagency agreement between the U.S. Department of Energy (DOE) and NSF. ORISE is managed for DOE by ORAU. All opinions expressed in this paper are the author's and do not necessarily reflect the policies and views of NSF, ORAU/ORISE, or DOE. 
The research was performed using computational resources sponsored by the Department of Energy's Office of Energy Efficiency and Renewable Energy and located at the National Renewable Energy Laboratory. 
This work was supported by the Department of Energy's Office of Science through the Exascale Computing Project (ECP), managed through Oak Ridge National Laboratory.




\end{acknowledgments}

\tableofcontents
\listoftables
\listoffigures
%\listofmusex


%\begin{listofsymbols}
%\end{listofsymbols}

\begin{listofabbrevs}
The following short list of abbreviations are used throughout this document. 
\begin{center}
\begin{tabular}{ll}
AMR& Adaptive Mesh Refinement \\
CFD& Computational Fluid Dynamics \\
CFL& Courant-Friedrichs-Lewy \\
CO2& Carbon Dioxide \\
DNS& Direct Numerical Simulation \\
DOE& Department of Energy \\
ECP& Exascale Computing Project \\
EoS& equation of state \\
HMHW& half-mean half-width \\
HPC& high-performance computing \\
LES& Large Eddy Simulation \\
MISDC& Multi-Implicit Spectral Deferred Correction \\
MOL& Method of Lines \\
NIST& National Institute of Standards and Technology \\
NREL& National Renewable Energy Laboratory \\
ODE& Ordinary Differential Equation \\
PDE& Partial Differential Equation \\
PPM& piecewise parabolic method \\
PR EoS& Peng-Robinson equation of state \\
QSSA& quasi-steady state assumptions \\
RANS& Reynolds-Averaged Navier-Stokes \\
rms& root mean square \\
SDC& Spectral Deferred Correction \\
sCO2& Supercritical Carbon Dioxide \\
SGS& Subgrid Scale \\
SMD& dynamic Smagorinsky \\
SRK EoS& Soave-Redlich-Kwong equation of state \\
TKE& Turbulent Kinetic Energy \\



\end{tabular}
\end{center}
\end{listofabbrevs}

\begin{abstract}
Supercritical Carbon Dioxide is of interest in a wide range of engineering problems, including carbon capture, utilization, and storage as well as advanced cycles for power generation. Non-ideal variations in physical properties of supercritical Carbon Dioxide impact the physics of these systems. It is important to understand how drastic changes in thermodynamic properties influence these flow physics in order to aid in and optimize the design of future technologies related to carbon capture and sequestration. In this study, we simulate turbulent supercritical Carbon Dioxide jets to gain a better understanding of these physics. Of particular interest is the impact of pseudo-boiling on supercritical flow dynamics. We use a second order finite volume method with adaptive mesh refinement as implemented in the reacting flow solver, \textit{PeleC}, to perform a Large Eddy Simulation of three turbulent jets of supercritical Carbon Dioxide. Additionally, we use the Soave-Redlich-Kwong equation of state to close the system and more accurately incorporate the departure from ideal gas behavior into the turbulent flow physics. We look at a variety of quantities of interest, including but not limited to axial velocity decay and spread, resolved Reynolds stress profiles at different downstream locations, and resolved turbulent kinetic energy along the axial direction of the flow. Across the three cases, the only parameters that vary are the temperature and density of the ambient fluid. One case is isothermal, where the jet and ambient fluid temperature are the same, while the other two cases are non-isothermal, with one involving injection crossing over the pseudo-boiling point and one with injection moving away from the pseudo-boiling point. Results are contrasted with established theory for ideal gas jets and similar numerical studies involving transcritical injection in order to capture the effects of widely varying thermal properties in the pseudo-critical region. We found that the isothermal supercritical jet exhibits many similar flow characteristics compared to ideal gas round turbulent jets, with minor differences seen in the decay and spreading rate of the jet and in a noticeable anisotropy between resolved turbulent kinetic energy components. The non-isothermal jet excluding the pseudo-boiling point exhibits only small difference compared to the isothermal case. The non-isothermal case involving the pseudo-boiling point displays markedly different behavior, with evidence indicative of increased Kelvin-Helmholtz-like instabilities and much faster jet decay and disintegration. These factors impact the degree of mixing in the transition region of the jet, leading to finer-scale vortices and faster transition to ambient properties.  
\end{abstract}

\mainmatter

\input Introduction
\input Model
\input Numerics
\input Simulations
\input Results
\input Conclusion

\renewcommand*{\appendixtocname}{Appendices} % For more than one appendix
\appendix
\input Transport_Appendix
\input Thermo_Appendix
\input Inputs_Appendix

% You have your choice of bibliography sections: either
% hand-crafted or BibLaTeX. The hand-crafted References
% section is enabled by default. Remove these entries if
% you're using BibLaTeX.

% This is the "hand-crafted" bibliography/references section:
%\begin{references}
%Mybib, Sample. \textit{An Example of a Bibliographic Entry
 %Created Manually}. Tallahassee, Florida: Fornish and Frak, 2010.

%Smith, Marigold. \textit{Lots and Lots of Bibliographic Entries
 %and How to Display Them}. Tallahassee, Florida: Gibson and Goulash, 2010.
%\end{references}

% Or use the BibLaTeX bibliography package, uncomment the lines in the
% preamble, and uncomment the \printbibliography line below. View the
% file 'myrefs.bib' to get a feel for what these entries may look
% like. See the document in the 'sample' folder for more citation and
% BibLaTeX examples.

\printbibliography

%\bibliography{myrefs}{}
%\bibliographystyle{plain}

\begin{biosketch}
Julia Ream was born and raised in Sarasota, FL. From an early age, Julia found math to be ``fun'', but didn't come to realize how uncommon that sentiment was until much later on in life. She started her undergraduate career at Florida State University in 2013, enrolling as an Exploratory student before committing to the Humanities and later on Theatre. Upon realizing that she missed doing math (weird), she added Applied Mathematics to her roster of majors. Although it took nearly 21 years, Julia eventually realized that she actually really liked math. So, after completing a Bachelor of Arts in Humanities and a Bachelor of Science in Mathematics, she decided to pursue her Doctoral degree in Applied and Computational Mathematics, also at Florida State University. 
\end{biosketch}

\end{document}
